---
title: "BasicReport"
author: Shimajiro
output:
  html_document:
    toc: true
    toc_float: false
    toc_depth: 2
    number_section: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)

library(tidyverse)
library(formattable)
```

```{r, include=F, cache=T}
source("../functions.R", encoding = "utf-8")

# Data Load
df.train <- load_train_data("../data/input/train_data.csv")
```

```{r, include=F}
cut_outof_ksd <- function(x, k=2) {
  avg_x <- mean(x, na.rm = T)
  sd_x  <- sd(x, na.rm = T)
  ifelse(abs(x - avg_x) > k * sd_x, NA, x)
}
```



# 基礎統計

## salary

```{r, include=F}
avg_salary <- mean(df.train$salary)
```


- 欠損: `r sum(is.na(df.train$salary))`
- 平均値: `r formattable::comma(avg_salary, digits = 0)`

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(salary)) +
    geom_histogram(binwidth = 10, colour = "white") +
#    geom_density(aes(y = ..count.. * 10), fill = "tomato", colour = "tomato", alpha = 1/3) +
    geom_vline(xintercept = avg_salary, linetype = 2, colour = "tomato", size = 1) +
    scale_x_continuous(limits = c(0, 1200)) +
    labs(
      y = NULL
    )
```


## position

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::count(position) %>%
  dplyr::mutate(ratio = n / sum(n)) %>%

  ggplot(aes(position, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_y_continuous(labels = scales::comma, limits = c(0, 8500)) +
    labs(
      y = NULL
    )
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = position), alpha = 1/2, show.legend = F) +
    labs(
      y = NULL
    ) +
    facet_grid(position ~ ., scales = "free_y")
```


## age

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age)) +
    geom_histogram(binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    )
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age)) +
    geom_histogram(aes(fill = position), binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    facet_grid(position ~ ., scales = "free_y")
```


### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(size = 0.75, alpha = 1/5)
```

#### education 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5) +
    geom_smooth(aes(colour = education), method = "lm") +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5) +
    geom_smooth(aes(colour = education), method = "lm") +
    scale_y_log10() +
    facet_grid(education ~ .)
```

#### position 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5) +
    geom_smooth(aes(colour = position), method = "lm") +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5) +
    geom_smooth(aes(colour = position), method = "lm") +
    scale_y_log10() +
    facet_grid(position ~ .)
```


## area

### カウント

```{r, fig.align="center", fig.width=8, fig.height=5}
df.train %>%

  dplyr::count(area) %>%
  dplyr::mutate(
    ratio = n / sum(n),
    area = forcats::fct_reorder(area, n)
  ) %>%

  ggplot(aes(area, n)) +
    geom_col() +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### salary との関係

```{r, fig.align="center", fig.width=8, fig.height=5}
df.train %>%
  dplyr::mutate(
    # 外れ値の除去
    salary = salary %>% cut_outof_ksd %>% cut_outof_ksd %>% cut_outof_ksd,
    area = forcats::fct_reorder(area, salary, na.rm = T)
  ) %>%

  ggplot(aes(area, salary)) +
    geom_boxplot() +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```


## sex

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::count(sex) %>%
  dplyr::mutate(
    ratio = n / sum(n)
  ) %>%

  ggplot(aes(sex, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = sex), alpha = 1/2, show.legend = T) +
    labs(
      y = NULL
    )
```


## partner

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::count(partner) %>%
  dplyr::mutate(
    ratio = n / sum(n)
  ) %>%

  ggplot(aes(partner, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = partner), alpha = 1/2, show.legend = T) +
    labs(
      y = NULL
    )
```


## num child

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::count(num_child) %>%
  dplyr::mutate(
    ratio = n / sum(n)
  ) %>%

  ggplot(aes(num_child, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_x_continuous(breaks = 0:9) +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
#    salary = salary %>% cut_outof_ksd %>% cut_outof_ksd %>% cut_outof_ksd,
    num_child = factor(num_child)
  ) %>%

  ggplot(aes(num_child, salary)) +
    geom_boxplot()
```


## education

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::count(education) %>%
  dplyr::mutate(
    ratio = n / sum(n)
  ) %>%

  ggplot(aes(education, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_y_continuous(labels = scales::comma, limits = c(0, 9000)) +
    labs(
      y = NULL
    ) +
    theme_gray(base_family = "Osaka") +
    theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(education, salary)) +
    geom_boxplot(aes(fill = education), alpha = 1/2, show.legend = F)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = education), alpha = 1/2, show.legend = F) +
    labs(
      y = NULL
    ) +
    facet_grid(education ~ ., scales = "free_y")
```


## service length

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length)) +
    geom_histogram(binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    )
```

#### position 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length)) +
    geom_histogram(aes(fill = position), binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    facet_grid(position ~ ., scales = "free_y")
```

#### education 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length)) +
    geom_histogram(aes(fill = education), binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    facet_grid(education ~ ., scales = "free_y")
```


### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length, salary)) +
    geom_jitter(size = 0.75, alpha = 1/5)
```

#### position 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm", show.legend = F) +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm", show.legend = F) +
    scale_y_log10() +
    facet_grid(position ~ .)
```

#### education 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = education), method = "lm", show.legend = F) +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(service_length, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = education), method = "lm", show.legend = F) +
    scale_y_log10() +
    facet_grid(education ~ .)
```


## study time

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time)) +
    geom_histogram(binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    )
```

#### position 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time)) +
    geom_histogram(aes(fill = position), binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    facet_grid(position ~ ., scales = "free_y")
```

#### education 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time)) +
    geom_histogram(aes(fill = education), binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    ) +
    facet_grid(education ~ ., scales = "free_y")
```


### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_boxplot(aes(x = factor(study_time)))
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_jitter(size = 0.75, alpha = 1/5)
```

#### position 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm") +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_jitter(aes(colour = position), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm") +
    scale_y_log10() +
    facet_grid(position ~ .)
```

#### education 別

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = education), method = "lm") +
    scale_y_log10()
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(study_time, salary)) +
    geom_jitter(aes(colour = education), size = 0.75, alpha = 1/5, show.legend = F) +
    geom_smooth(aes(colour = education), method = "lm") +
    scale_y_log10() +
    facet_grid(education ~ .)
```



## commute

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(commute)) +
    geom_histogram(binwidth = 0.25, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    )
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(commute, salary)) +
    geom_jitter(size = 0.75, alpha = 1/5)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(commute, salary)) +
    geom_jitter(aes(colour = partner), size = 0.75, alpha = 1/5) +
    scale_y_log10()
```

## overtime

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(overtime)) +
    geom_histogram(binwidth = 1, colour = "gray") +
    scale_y_continuous(labels = scales::comma) +
    labs(
      y = NULL
    )
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(overtime, salary)) +
    geom_jitter(size = 0.75, alpha = 1/5)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(overtime, salary)) +
    geom_jitter(aes(colour = partner), size = 0.75, alpha = 1/5)
```


## 新卒フラグ

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      d == 2 ~ "d_2",
      d == 3 ~ "d_3",
      d == 4 ~ "d_4",
      d == 5 ~ "d_5",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:5, sep = "_"), "others"))
  ) %>%
  dplyr::count(flg) %>%
  dplyr::mutate(ratio = n / sum(n)) %>%

  ggplot(aes(flg, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    labs(
      x = NULL,
      y = NULL
    )
```

### salary との関係

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:1, sep = "_"), "others"))
  ) %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = flg), alpha = 1/2, show.legend = F) +
    facet_grid(flg ~ ., scales = "free_y") +
    labs(
      x = NULL,
      y = NULL
    )
```


# 2変数間の関係

## partner & num child

```{r}
df.train %>%

  dplyr::count(partner, num_child) %>%
  dplyr::mutate(n = formattable::comma(n, digits = 0)) %>%
  tidyr::spread(key = num_child, value = n, fill = 0L) %>%

  knitr::kable(
    format = "html",
    align = "c"
  ) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped"), full_width = F, position = "center") %>%
  kableExtra::add_header_above(c(
    " " = 1,
    "num child" = 10
  ))
```

### カウント

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    partner_child = ifelse(partner == 0, "no_partner", stringr::str_c("child", num_child, sep = "_")) %>%
      factor(levels = c(
        "no_partner",
        stringr::str_c("child", 0:9, sep = "_")
      ))
  ) %>%

  dplyr::count(partner_child) %>%
  dplyr::mutate(ratio = n / sum(n)) %>%

  ggplot(aes(partner_child, n)) +
    geom_col() +
    geom_text(aes(label = formattable::percent(ratio, digits = 1)), vjust = -0.5) +
    scale_y_continuous(labels = scales::comma, limits = c(0, 11000), breaks = seq(0, 10000, 2500)) +
    labs(y = NULL)
```

### salary との関係

```{r, fig.align="center", fig.width=6, fig.height=9}
df.train %>%

  dplyr::mutate(
    partner_child = ifelse(partner == 0, "no_partner", stringr::str_c("child", num_child, sep = "_")) %>%
      factor(levels = c(
        "no_partner",
        stringr::str_c("child", 0:9, sep = "_")
      ))
  ) %>%

  ggplot(aes(salary)) +
    geom_density(aes(fill = partner_child), alpha = 1/2, show.legend = F) +
    labs(y = NULL) +
    facet_grid(partner_child ~ ., scales = "free_y")
```


## 新卒フラグ & age

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:1, sep = "_"), "others"))
  ) %>%

  ggplot(aes(age, salary)) +
    geom_point(aes(colour = flg), alpha = 1/3) +
    geom_smooth(aes(colour = flg), method = "lm") +
    facet_grid(flg ~ .)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:1, sep = "_"), "others"))
  ) %>%

  ggplot(aes(age, salary)) +
    geom_point(aes(colour = flg), alpha = 1/3) +
    geom_smooth(aes(colour = flg), method = "lm")
```

## 新卒フラグ & service length

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:1, sep = "_"), "others"))
  ) %>%

  ggplot(aes(service_length, salary)) +
    geom_point(aes(colour = flg), alpha = 1/3) +
    geom_smooth(aes(colour = flg), method = "lm") +
    facet_grid(flg ~ .)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  dplyr::mutate(
    base_age = dplyr::case_when(
      education == 0 ~ 18,
      education == 1 ~ 20,
      education == 2 ~ 22,
      education == 3 ~ 24,
      education == 4 ~ 27
    ),
    d = age - base_age - service_length,
    flg = dplyr::case_when(
      d == 0 ~ "d_0",
      d == 1 ~ "d_1",
      T      ~ "others"
    ) %>%
      factor(levels = c(stringr::str_c("d", 0:1, sep = "_"), "others"))
  ) %>%

  ggplot(aes(service_length, salary)) +
    geom_point(aes(colour = flg), alpha = 1/3) +
    geom_smooth(aes(colour = flg), method = "lm")
```


## position & age

```{r, fig.align="center", fig.width=7, fig.height=9}
df.train %>%

  dplyr::mutate(
    salary = salary %>%
      cut_outof_ksd %>%
      cut_outof_ksd %>%
      cut_outof_ksd
  ) %>%

  dplyr::mutate(
    age_segment = dplyr::case_when(
      age <= 20 ~ "age_lte_20",
      dplyr::between(age, 21, 30) ~ "age_21_30",
      dplyr::between(age, 31, 40) ~ "age_31_40",
      dplyr::between(age, 41, 50) ~ "age_41_50",
      dplyr::between(age, 51, 60) ~ "age_51_60",
      T                           ~ "age_gte_61"
    ) %>%
      factor(levels = c(
        "age_lte_20",
        "age_21_30",
        "age_31_40",
        "age_41_50",
        "age_51_60",
        "age_gte_61"
      ))
  ) %>%

  ggplot(aes(position, salary)) +
    geom_boxplot(aes(fill = position), alpha = 1/2, show.legend = F) +
    facet_grid(age_segment ~ .)
```

```{r, fig.align="center", fig.width=7, fig.height=9}
df.train %>%

  dplyr::mutate(
    salary = salary %>%
      cut_outof_ksd %>%
      cut_outof_ksd %>%
      cut_outof_ksd
  ) %>%

  dplyr::mutate(
    age_segment = dplyr::case_when(
      age <= 20 ~ "age_lte_20",
      dplyr::between(age, 21, 30) ~ "age_21_30",
      dplyr::between(age, 31, 40) ~ "age_31_40",
      dplyr::between(age, 41, 50) ~ "age_41_50",
      dplyr::between(age, 51, 60) ~ "age_51_60",
      T                           ~ "age_gte_61"
    ) %>%
      factor(levels = c(
        "age_lte_20",
        "age_21_30",
        "age_31_40",
        "age_41_50",
        "age_51_60",
        "age_gte_61"
      ))
  ) %>%

  ggplot(aes(age_segment, salary)) +
    geom_boxplot(aes(fill = position), alpha = 1/2, show.legend = F) +
    facet_grid(position ~ .)
```


```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(alpha = 1/3, aes(colour = position), alpha = 1/3, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm") +
    facet_grid(position ~ .)
```

```{r, fig.align="center", fig.width=7, fig.height=5}
df.train %>%

  ggplot(aes(age, salary)) +
    geom_jitter(alpha = 1/3, aes(colour = position), alpha = 1/4, show.legend = F) +
    geom_smooth(aes(colour = position), method = "lm", size = 2)
```

## position & education

```{r, fig.align="center", fig.width=7, fig.height=9}
df.train %>%

  dplyr::mutate(
    salary = salary %>%
      cut_outof_ksd(k = 4)
  ) %>%

  ggplot(aes(y = salary)) +
    geom_boxplot(aes(fill = position), show.legend = F) +
    facet_grid(position ~ education)
```

## position & sex

```{r}
df.train %>%

  dplyr::group_by(position, sex) %>%
  dplyr::summarise(
    n = n(),
    ratio_salary = mean(salary, na.rm = T) / avg_salary
  ) %>%
  dplyr::ungroup() %>%

  ggplot(aes(position, sex)) +
    geom_tile(aes(fill = ratio_salary), colour = "black") +
    scale_fill_gradient2(low = "blue", mid = "white", high = "tomato", midpoint = 1) +
    geom_text(aes(label = formattable::percent(ratio_salary, digits = 0)), colour = "black", size = 5) +
    geom_point(aes(size = n), colour = "gray", alpha = 1/3, show.legend = F) +
    scale_size_area(max_size = 35)
```

